### 2009-10-28 doc/tech_doc/jura/jura-tech-doc.tex
Installation instructions: Win compatibility

A-REX executes the reporting executable through the file ``logger'' in
the \textit{libexec/arc} directory under the install location (this is
an A-REX legacy kept for backwards compatibility with the old
logger). Therefore, to enable automatic periodic reporting, a symbolic
link called ``logger'' should be placed in \textit{libexec}, pointing
to the JURA executable.

>>>>

A-REX executes the reporting executable through the file
``\textit{logger}'' in the \textit{libexec/arc} directory under the
install location (this is an A-REX legacy kept for backwards
compatibility with the old logger). Therefore, to enable automatic
periodic reporting, the ``\textit{jura}'' executable file should be
copied into \textit{libexec/arc}, or if possible, a symbolic link
called ``\textit{logger}'' should be created there, pointing to the
``\textit{jura}'' executable.
